%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Arshpreet}{Singh}
\title{Lead Engineer}                               % optional, remove / comment the line if not wanted
\address{Address: SBP COD, 1105, Chandigarh, India}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+91 991 5959387}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{arsh840@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{www.github.com/arshpreetsingh}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\quote{Avoiding complexity reduces bugs.}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\small{I am actively developing and maintaining internal \textbf{Python and Golang-based distributed systems} that are held
responsible for index-creation, data-fanout, index-rebalance, and portfolio-generation pipelines at Blackrock Inc. I do
actively participate in solution architecture and Cloud implementation of legacy systems.


I have 6+ years of experience as a \textbf{Python developer}, with expertise in \textbf{Flask}, \textbf{Django, SQL, Golang, Latex, C/C++,
Julia, and parallelization using MPI.} I have worked on multi-processing techniques using cutting-edge asynchronous
programming models. I have also contributed to several \textbf{Open-Source} projects like \textbf{Tux4Kids}, \textbf{Kivy}, \textbf{Open-Street
Mappings}, \textbf{Pennylane}(Quantum-Computing Framework), and \textbf{Paraview}(Scientific Data-Analysis Framework).


\section{Employment Details}

\vspace{6pt}

\begin{itemize}

\item{\cventry{April 2020--Current}{Lead Engineer, client: Blackrock}{ITC Infotech }{Remote Work}{}
{\vspace{3pt}
\cvlistitem{Development of \textbf{5+ data-processing applicaions} using Python, Go-lang, Docker, and Kubernetes.}
\cvlistitem{Responsible for onboarding \textbf{2 major vendors(Morgan Stanley Capital International and Financial Times Stock Exchange)} onto customer proprietary end-to-end investment
platform.}
\cvlistitem{Development and integration of  index-market holiday framework for \textbf{100+ index vendors} that reduced failure of production jobs by 80\%.}
\cvlistitem{Hired, Trained, and onboarded 5+ Associate level Engineers for clients like Gartner, Blackrock, and Wallmart.}
\cvlistitem{Legacy code maintainer for 3 python projects related to index rebalances.}
\cvlistitem{Development of Unit-Testing modules.}
\cvlistitem{Delivered Talk on \textbf{Quantum-Computing and Hybrid-Machine-Learning} at Blackrock internal Python conference.}
}}

\vspace{6pt}

\item{\cventry{January 2019-- April 2020}{GoLang Developer, client: Multiple}{Maropost India}{}{}{\vspace{3pt}
\cvlistitem{Development and Deployment \textbf{20+ Microservices} using Technology Stack: Go-lang, Protocol Buffers, Kafka,
Docker, Kubernetes, and TimescaleDB.}
\cvlistitem{Responsible for managing GCP and generic infrastructure for High Availability.}
\cvlistitem{Replaced \textbf{4 RoR(Ruby on Rails) Services with GoLang} to reduce server response time and increase efficiency by 70\%.}
\cvlistitem{Solely responsible for \textbf{containerization(Docker) of 10+ projects}, Also initiated container technology in the organization with internal meetups and hackathons.}
}}

\vspace{6pt}

\item{\cventry{August 2017--April 2018}{Senior Software Engineer}{Netsmartz India}{}{}{\vspace{3pt}
\cvlistitem{Development and Deployment of MicroServices using Technology Stack: \textbf{Python, Flask, Docker, and MySQL.} Implemented asynchronous programming models to reduce response time from 5 minutes to 15 seconds.}
\cvlistitem{Development of an in-house framework to achieve Periodic Automation Testing for the complete SDN platform that increased availability of production systems.}
\cvlistitem{Worked on BlockChain Project using Hyperledger to build network-packet pathways for transparent and
secure loop.}}}

\vspace{6pt}

\item{\cventry{May 2016--August 2017}{Full-Stack Python. Client: Bitfinex}{Revinfotech Ludhiana}{}{}{\vspace{3pt}
\cvlistitem{Design and development of Software Projects using Python, Django, Flask, MongoDB.}
\cvlistitem{Active participation with 6+ clients
to understand business needs and creation of end-to-end Solutions contributed as a major revenue source.}}}

\item{\cventry{January 2014--April 2016}{Web Developer. Client: Mutiple}{Future Tech IT center Ludhiana}{}{}{\vspace{3pt}
\cvlistitem{ Design and development of Software Projects using Python, HTML, CSS and Wordpress}
\cvlistitem{ Active participation with clients to understand business needs and Producing end to end Solutions.}}}

\end{itemize}

%\newpage

\section{Noteable Projects}

\vspace{5pt}

\begin{itemize}

\item{\textbf{Development and Deployment of Index-Cache-Server using Golang} \textit{}

\vspace{3pt}

\small{This project was required to cache 30 days of Indices data to deliver over \textbf{100+ clients and reduce request load on the actual database server.}}}

\item{\textbf{MSCI data pipeline development} \textit{}

\vspace{3pt}

\small{Developed index data-loader for \textbf{MSCI(Morgan Stanley Capital International)} to handle Quality-Check and Asset-Resolution for Index-vendors.}}

\vspace{6pt}

\item{\textbf{Development of Hybrid Quantum Machine-Learning Model(Tensorflow-Quantum)} \textit{}

\vspace{3pt}

\small{Used Pennylane Quantum Framework to create Quantum Machine Learning Model to run on actual near term Quantum-Computer model enhances the prediction accuracy of Classical model by 20\%.}}

\vspace{6pt}
\item{\textbf{Neural Network based crypto trading bot}

\vspace{3pt}

\small{Bitcoin Live Trading is a Web-Based System developed using Django to generate Buy/Sell
calls using Bitfinex and Coindesk APIs based on Predictive Results produced by Neural Network Algorithm.}}

\vspace{6pt}

\item {\textbf{Market-Swing Auto-Trading Algorithm}

\small{Worked on Technical-Analysis for high momentum stocks and produced trading strategy with more than 50\% annual results on backtests.}}

\item{\textbf{ParaView Advanced Volume Filter(Scientific Data Analysis)}

\vspace{3pt}

\small{Advanced Volume Filter developed using Python as Scripting Language
with support of other Libraries like Numpy, Scipy, and SymPy to filter different types of materials automated everyday manual work of 8+ hours into 20 minutes.
}}

\end{itemize}

\section{Education and Certifications}

\vspace{5pt}

\subsection{Academic Qualifications}

\vspace{5pt}

\begin{itemize}

\item{\cventry{2009--2013}{{B.Tech: Information Technology}}{\textit{}}{GNDEC - Ludhiana, Punjab, India}{}{\textit{}}{}}

\end{itemize}


\subsection{Certifications}

\vspace{5pt}

\begin{itemize}

\item{\cventry{2020}{https://bit.ly/3m87lih}{Coursera - Tensorflow Specilization for Developers}{}{}{}}

\item{\cventry{2020}{https://bit.ly/3qunH5C}{IBM - Quantum Computing Foundations}{}{}{}}

\item{\cventry{2020}{https://www.hackerrank.com/certificates/b43d16c9c3c4}{HackerRank - Rest APIs Development}{}{\textit{}}{}}

\item{\cventry{2017}{https://bit.ly/3A2QmTC}{Coursera - Julia for Scientific Programming }{}{\textit{}}{}}

\item{\cventry{2017}{https://bit.ly/2UAxHOx}{Coursera - Deep Learning Specialization}{}{\textit{}}{}}

\item{\cventry{2020}{https://bit.ly/3xVYm6V}{Pluralsight - Golang Fundamentals and Beyond}{}{\textit{}}{}}

\item{\cventry{2020}{https://bit.ly/2TbZ3dv}{Pluralsight - Working with Graph Algorithms in Python}{}{\textit{}}{}}

\item{\cventry{2020}{https://bit.ly/3jcrOS5}{Pluralsight - The Challenges of Quantum Computing}{}{\textit{}}{}}

\item{\cventry{2020}{https://bit.ly/3x1dpMx}{Pluralsight - Applying Financial Risk-Modeling Techniques}{}{\textit{}}{}}

\item{\cventry{2020}{https://bit.ly/35Y7BaA}{Pluralsight - Docker and Kubernetes}{}{\textit{}}{}}

\item{\cventry{2020}{https://www.redhat.com}{Redhat - Fundamentals of Containers DO081X}{}{\textit{}}{}}

\end{itemize}

\vspace{2pt}


\section{Open Source Contributions}

\vspace{6pt}

\begin{itemize}

\item \textbf{Container-Orchestration of Quantum ML Framework}

\vspace{3pt}

Development of Container-Orchestration for \href{https://github.com/PennyLaneAI}{Pennylane} to support
multiple Quantum-interfaces with single space and one click installation for CPU and GPU devices.

\vspace{6pt}

\item \textbf{Quantum Simulator development for Quantum-Computing Platform(Unitary Hack) }
\vspace{3pt}

Participated in Unitary-Hack\textbf{(https://unitaryfund.github.io/unitaryhack/)} for the development of
Quantum-Simulator for Pytorch. After this contrbution end-user will be able to perform Quantum-Operations
on Quantum-Devices using Pytorch as backend, which makes Quantum Circuits trainable as Pytorch tensors.

\vspace{6pt}

\item \textbf{Tuxblocks}
\vspace{3pt}

Tux Paint and Tuxmath are free,
award-winning programs for \textbf{children ages 3 to 12} (for example, preschool and K-6).
Tux Paint is used in schools around the world as a computer literacy drawing activity.
It combines an easy-to-use interface, fun sound effects,
and an encouraging cartoon mascot who guides children.

\vspace{6pt}

\item \textbf{Open Street Mapping}

\vspace{3pt}

OpenStreetMap is a map of the world, created by people and free to use under an open license.
I Organized a \textbf{"Mapping Party"} as well as Workshop for School students to tech \textbf{GPS-Tracking} ,
Uploading and Creating maps using GPS trace.
Completed Digital mapping of 20 villages of Punjab with help of school students.

\vspace{6pt}

\item \textbf{Rock's Cluster Implementation(High Performance Computing)}

\vspace{3pt}

Rocks is an open-source Linux cluster distribution that enables end users to easily
build computational clusters,
 grid endpoints and visualization tiled-display walls.

\textbf{Built complete HPC(High Performance Computing)Cluster} using 10 computers and HPC
module was used to distribute jobs throughout the compute nodes.

\vspace{6pt}

\item \textbf{LTSP(Linux Trminal Server Project) Implementation}
\vspace{3pt}

The Linux Terminal Server Project adds thin client support to Linux servers. LTSP is a flexible,
 cost effective solution that is empowering schools, businesses,
 and organizations all over the world to easily install and deploy thin clients.

My Project AIM was to setup Load-balancer, boot-server as well as application
server. Boot server was responsible for providing Boot image to each client as
well as helping to allocate it to Application Server.

\end{itemize}


% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
