%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{purple}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Amberpreet}{Kaur}
\title{Asst. Professor}                               % optional, remove / comment the line if not wanted
\address{Address: Highland Park Homes, Zirakpur}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+91 842 7260360}                   % optional, remove / comment the line if not wanted
%\phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{amber2814@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{BDS, MDS (Oral and Maxillofacial Pathology and Oral Microbiology)}                         % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
\quote{It's better to know how to learn than to know.}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

The objective of my career is to excel in the field of \textbf{Oral Pathology and Microbiology} and to work with an
organization where I can contribute my skills to the development of the organization and enhance
my knowledge and henceforth to \textbf{serve society} in the best way.



\vspace{5pt}
In my professional career, I have worked on wide nature of skillsets which includes \textbf{Hematological investigations},
Clinical consultations of patients with \textbf{Oral and Maxillofacial Pathologies}, \textbf{Cytology}(Patient
selection, smear, and reporting) and \textbf{Histopathology}(Clinical examination, biopsy, processing and reporting).

\section{Employment Details}

\begin{itemize}

\item{\cventry{April 2020--Current}{Assistant Professor}{MMCDSR, Mullana}{Ambala, India}{}
{
\cvlistitem{Serving as an Assistant-Professor in the department of \textbf{Oral and Maxillofacial Pathology and Oral Microbiology}}
\vspace{3pt}
\cvlistitem{Theory teaching on \textbf{Oral Pathology, Oral Microbiology and Forensic Dentistry} for BDS students.}
\vspace{3pt}
\cvlistitem{Conducting practical exams and viva for BDS students.}
\vspace{3pt}
\cvlistitem{Grossing and reporting duty for allotted period of time}
\vspace{3pt}
\cvlistitem{Assessment of the \textbf{Seminars and Posters for UG and PG students}}
\vspace{3pt}
\cvlistitem{\textbf{NAAC} coordinator}
}}
\end{itemize}

%\newpage

\section{Education and Publications}

\subsection{Academic Qualifications}

\begin{itemize}

\item{\cventry{2018--2021}{{MDS (Oral and Maxillofacial Pathology and Oral Microbiology)}}{\textit{}}{Dr. H.S. Judge, Panjab University}{}{\textit{}}{}}

\item{\cventry{2012--2017}{{BDS}}{\textit{}}{DBDC Mandi, Gobindgarh,Punjab}{}{\textit{}}{}}

\item{\cventry{2012--2017}{{Class XII}}{\textit{}}{S.D. College, Barnala, Punjab}{}{\textit{}}{}}

\item{\cventry{2012--2017}{{Class X}}{\textit{}}{S.D.P.S. Barnala, Punjab}{}{\textit{}}{}}

\end{itemize}


\subsection{Publications}

\begin{itemize}
    \item{\cventry{}{{(a)Khangura AK, Gupta S, Gulati A, Singh S. Tooth decalcification using different decalcifying agents}}{\textit{}}{2020}{}{\textit{}}{}}

     A comparative study. J Oral Maxillofac Pathol 2021;25:463-9.


    \item{\cventry{}{{(b)Khangura, A. K., Gupta, S., Mehta, M., and Gulati,(2022)}}{\textit{}}{2022}{}{\textit{}}{}}

    Isolation and Identification of Various Candida Species in Potentially Malignant Disorders of Oral Cavity: A Retrospective
Study. International Journal of TROPICAL DISEASE and Health, 43(6), 32-44.

    \item{\cventry{}{{(c)Amberpreet Kaur K., Shally Gupta.}}{\textit{}}{2022}{}{\textit{}}{}}

     Pediatric soft tissue lesions. Updent publication, Bijnor. ISBN: 978-81-959014-0-1 (2022).


\end{itemize}

\section{Conference and Conventions Attended}

\begin{itemize}

\item \textbf{XVII National IAOMP postgraduate Convention}

7th and 8th July 2018, Sri Ramachandra
Medical College and Research Institute, Chennai. I attended Hands on workshop on “Biopsy techniques: Basics and Application” at Sri
Ramachandra Medical College and Research Institute, 2018, Chennai.

\vspace{3pt}

\item \textbf{XXVII National IAOMP Conference}

16th -18th November 2018, Amritsar (Punjab),
India. I attended hands on training workshop on “PCR and Real time PCR” at XXVII National
IAOMP Conference, Amritsar 2018.

\vspace{3pt}
\item \textbf{6th Indian Pacific Academy of Forensic Odontology}

World Conference 15th -17th
February, 2019, Chandigarh.
\vspace{3pt}
\item \textbf{XXVIII IAOMP National Conference}

1st - 3rd November, 2019, Kovalam ,Thiruvanabthapuram.

\vspace{3pt}
\item \textbf{18th National Triple O Symposium and 4th International Oral Pre – Cancer Congress}

6th – 8th March 2020 ,MAIDS New Delhi.

\vspace{3pt}
\item \textbf{ICONICA 2020 A Global Summit on Next Gen Paradigms in Health Care}

12th – 14th February 2020, Panjab University, Chandigarh, India.

\vspace{3pt}
\item \textbf{29th edition of the National Conference of Indian Association of Oral and Maxillofacial
Pathologists}

Dehradun, Uttarakhand, 11th-13th November 2022.
    \vspace{3pt}
\end{itemize}



\section{Paper and Poster Presentation}
\begin{itemize}

\vspace{3pt}
\item {\textbf{Paper - “Rare Opportunistic Fungal Infections of Oral and Maxillofacial Region:} A
Review” XXVII National IAOMP Conference, Amritsar 2018.}
\vspace{3pt}
\item {\textbf{Paper – “Tooth Decalcification Using Different Decalcifying Agents:} A comparative
Study” 18 th National Triple O Symposium and 4 th International Oral Pre – Cancer and
Cancer Congress, 2020 New Delhi}
\vspace{3pt}
\item {\textbf{Paper - “Recent Advancements in Exfoliative Cytology for Oral Potentially
Malignant Disorders and Malignancy”} XXVIII IAOMP National Conference, 2019,
Kovalam, Thiruvananthapuram.}
\vspace{3pt}
\item {\textbf{Poster - “Determination of stature using Teeth”} 6 th INPAFO World Conference, 2019
Chandigarh.}
\vspace{3pt}
\item{\textbf{Poster - “Peripheral blood smear} – An important investigation for the initial diagnosis
of hemoglobinopathies” XVII IAOMP Postgraduate Convention 2018, Chennai.}
\vspace{3pt}
\item {\textbf{Poster- “The Spindle Cell Neoplasm of Head And Neck Region:} A Systematic
Review” Indian Association Of Oral and Maxillofacial Pathologists, online National
Scientific Competition for Postgraduates 2020.}
\end{itemize}


\section{Awards}
\begin{itemize}
    \item
    \vspace{3pt}
    \textbf{Overall Best Scientific Poster Award Review} - “Peripheral blood smear – An
important investigation for the initial diagnosis of hemoglobinopathies” at XVII
IAOMP Postgraduate Convention 2018, Chennai.
    \item
    \vspace{3pt}
\textbf{Best Scientific Poster Award Review} –“Determination of stature using Teeth” at 6 th
INPAFO World Conference, 2019 Chandigarh.
\end{itemize}



\section{Patents and Copyrights}
\begin{itemize}
\item{\textbf{}} \textit{\textbf{Khangura Kaur Amberpreet}, Nayak Sushruth, Nayak Prachi, Pathak
Kush, Himanshi, 2022, Grossing table, 42/2022, Intellectual Property India. And omit
‘haematological investigations’ from this point.}
\end{itemize}


\vspace{300pt}
\textbf{DECLARATION:}
I hereby declare that all the statements made herein are true to best of my knowledge and
belief.

\textbf{Dr. Amberpreet Kaur Khangura}
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
